Bioverse: Origins of Life

### 2024-07-12 src/tex/ms.tex
add intro for Discussion

\section{Discussion}
\label{sec:discussion}
%''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''
\subsection{Constraining power for the origins of life as a function of biosignature location}
\todo[inline]{How does the location of biosignature detections impact the credibility of OOL scenarios?}
\todo[inline]{biosignature on M~dwarf planet vs. FGK: Impact on UV flux requirement?}
The cyanosulfidic scenario, in particular its predicted existence of a minimum \gls{NUV} flux required for prebiotic chemistry, offers an opportunity to test an origins of life hypothesis with a statistical transit survey sampling planets with varying \gls{NUV} flux histories.
It comes to no surprise that the success rate of such a test is sensitive to the sample size of the survey and to the occurrence of life on temperate exoplanets.
As we have shown, the statistical power of this test also depends on the distribution of past \gls{NUV} fluxes in the sample and on the required threshold flux.
Optimizing the survey to sample a wide range of NUV flux values, particularly at the extremes, can enhance the likelihood of obtaining strong evidence for or against the hypothesis.
Intermediate values of the threshold \gls{NUV} flux are more likely to yield strong evidence than extreme values, as the dataset under the alternative hypothesis $H_1$ differs more from the null hypothesis in this case while still being sufficiently populated.
The required threshold flux is, of course, a priori unknown and we cannot influence it.
If, however, better theoretical predictions for the required \gls{NUV} flux for abiogenesis become available, the survey strategy can be further optimized, for instance by targeting planets that are estimated to have received a \gls{NUV} flux slightly below and above this threshold.

An interesting  aspect lies in the distribution of host star spectral types:
Under the \gls{NUV} hypothesis, the occurrence of life is expected to correlate with the host star's spectral type, with late-type M~dwarfs being favored due to their higher \gls{NUV} fluxes in the \gls{HZ}~\citep{Richey-Yowell2023}.
However, the distribution of maximum past \gls{NUV} fluxes in this sample is narrow in this sample, which may limit the constraining power of the survey depending on the (unknown) threshold \gls{NUV} flux.
An M~dwarf sample may help to test the high \gls{NUV} flux end of the hypothesis; a higher occurrence of biosignatures here would support the hypothesis that a higher NUV flux is beneficial or necessary for life.

FGK stars, on the other hand, show a wider distribution of maximum past \gls{NUV} fluxes in the \gls{HZ}, which may increase the likelihood of obtaining strong evidence for or against the hypothesis.
With this sample, the survey will be more sensitive to the low \gls{NUV} flux end of the hypothesis.
A lack of biosignatures on these planets would support the \gls{NUV} hypothesis, whereas their presence might suggest that lower NUV fluxes are also sufficient for abiogenesis or indicate different abiogenic pathways. CITE

%\subsection{What do we learn from a single biosignature detection?}
%\todo[inline]{discuss constraining power on OOL of a convincing biosignature detection on a single planet, depending on the position of the planet in the parameter space we explored.}

>>>>

\section{Discussion}
\label{sec:discussion}
A key question in the quest to understand the origins of life is which natural processes best explain how living matter spontaneously appears from nonliving matter~\citep{Malaterre2022}.
The cyanosulfidic scenario~\citep{Patel2015}, in particular its predicted existence of a minimum \gls{NUV} flux required for prebiotic chemistry, seems to offer an opportunity to test an origins of life hypothesis with a statistical transit survey sampling planets with varying \gls{NUV} flux histories.
In the following, we discuss the prospects of testing the UV hypothesis in light of our results.
